Testing and Isolation Efficacy: Insights from a Simple Epidemic Model

### 2021-04-27 SIR_manuscript.tex
seperating params and the functions, make rda, create make rull for functions, minor changes in mans results sec

The explicit formula for the basic reproduction number, $\Rnum$ \eqref{R0}, provides an opportunity to study the influence of changes in the underlying parameters on the critical index of epidemic dynamics. We are interested in exploring the effect of parameters that could be manipulated by public-health policy, including the isolation efficacy parameters, $\theta\_c$ and $\theta\_w$, \percap testing intensity, $\rho$, and the rate of test return, $\omega$. In this context, two testing strategies, namely random and targeted testing, were explored.

>>>>

The explicit formula for the basic reproduction number, $\Rnum$ \eqref{R0}, provides an opportunity to study the influence of changes in the underlying parameters of interest on the critical index of epidemic dynamics. These parameters include the isolation efficacy parameters, $\theta\_c$ and $\theta\_w$, \percap testing intensity, $\rho$, and the rate of test return, $\omega$. In this context, two testing strategies, namely random and targeted testing, were explored.

### 2021-04-27 note/SIR_scrap.tex
seperating params and the functions, make rda, create make rull for functions, minor changes in mans results sec

>>>>

\section{Unused Scripts}
# Conditional stop for ODE desolver
# rootfun <- function (time, state,params) {
#   unpack(as.list(c(state,params)))
#   return(I_u - 1) }

# ode(
#   func=sir.model,
#   y=state_init,
#   times= d,
#   parms=params,
#   atol = 1e+1, rtol = 1e+1
#   rootfun = rootfun,
#   method="lsodar"
# )

## R0 expression with eta_w/eta_c factored
# R02 <- function(state=state_dfe,params){
#   unpack(as.list(c(state,params)))
#   Sn <- Sn_dfe(params)
#   Su <- Su_dfe(params)
#   Fi <- Fi_hat(params) #at DFE
#
#   A2 <- gamma*(p_I*Fi*omega*Sn+(omega+gamma)*(gamma*Sn+Fi*N0))
#   B2 <- p_I*Fi*omega*(gamma*Su+omega*N0)
#   D <- gamma*(omega+gamma)*(gamma*Su+omega*N0)
#   C2 <- beta/((N0*gamma*(gamma*(omega+gamma)+Fi*(gamma+omega*p_I)))*(omega+gamma))
#   # s <- eta_w/eta_c
#   return((eta_c*(s*A2+B2)+D)*C2)
# }
# eval_R0 <- function(state=state_dfe,params){
#   ## input the params and their range, this function makes a grid dataframe, calls R0 and outputs the csv file
#   ## the params are defaults, specify the range of favorite params here.
#   unpack(as.list(c(state,params)))
#   tol <- 1e-10 ## to resolve the issue of very small numbers
#   # specify the ranges, FIXME, not to be hard coded!
#   eta_w <- seq(0,1, length.out=n_out)
#   eta_c <- seq(0,1, length.out=n_out)
#   rho <- seq(0,0.01, length.out=n_in) ## 0,0.01
#   omega <- seq(0.1,2 , length.out=n_in) #note omega must be > rho, was 0.1 to 2
#
#   df1 <- expand.grid(N0=params[["N0"]],beta=params[["beta"]],gamma=params[["gamma"]],omega=omega,rho=rho,
#                      W_S=W_S,W_I=params[["W_I"]],W_R=params[["W_R"]],
#                      p_S=params[["p_S"]],p_I=params[["p_I"]],p_R=params[["p_R"]],
#                      eta_w=eta_w,eta_c=eta_c)
#   df2<- data.frame(df1,
#                    R0=apply(df1,1,function(params_in)R0(params=params_in)),
#                    Fi= apply(df1,1,function(params_in)Fi_hat(params=params_in)))
#   # This is for plotting purposes:
#   df2 <- (df2 %>%
#             dplyr::mutate(R0_sub=ifelse(eta_w<eta_c, NA, R0),
#                           theta_w=1-eta_w,
#                           theta_c=1-eta_c,
#                           Delta=ifelse(eta_w<eta_c, NA, 1-(R0*gamma/beta) ),
#                           Delta=ifelse(abs(Delta)<tol,0,Delta)
#                           )
#           )
#   return(df2)
# }

# state_init <- c(S_u=params[["N0"]], S_n=0,
#                 I_u=1,I_n=0,I_p=0,I_t=0,
#                 R_u=0,R_n=0,R_p=0,R_t=0,
#                 N=0,P=0)

# state_dfe <- c(S_u=Su_dfe(params), S_n=Sn_dfe(params),
#                 I_u=0,I_n=0,I_p=0,I_t=0,
#                 R_u=0,R_n=0,R_p=0,R_t=0,
#                 N=0,P=0)
